\section{Results and discussion}\label{res}

\subsection{Material}

\begin{description}
\item [Machine] 1$\times$CPU 2.90GHz
\item [FEM] Resolution of the weak problem in $\chi$ was done with FEniCS, %
an open-source platform programmed in Python designed for Finite Element Method.
\item [ROM] The numpy package of python 3 was used for POD.
\end{description}

\subsection{Two-dimensional case : varying the radius of a single circular inclusion}
\input{res_disc/res_dim2.tex}

%\Floatbarrier
\subsection{Three-dimensional case}

Following geometries, especially when the number of nodes in the mesh where Finite Element vector space is defined, fully justify the use of a Reduced Order Model, %
sice time of execution of the Finite Element Method becomes significant.

\par
Like in section \ref{hom_d}, we have chosen three different resolutions of the meshes used for each problem to solve with a ROM. %
These are defined by the number of nodes : $10$, $20$ or $50$, we find on a side of the unit cube.

\par
The following table gives the values of $N_{rom}$ with a threshold of $99,99\%$. We can see that, for a same problem in $\chi (\rho ,\mathbf{y})$, %
$N_{rom}$ depends on the size of the mesh : %
this can be understood mathematically since it has been defined, and calculated, from a Finite Element space. %
The latter is nothing more than an approximation of $L^2$ or $H^1$ we use for our physical problem.

\par
Therefore the physically relevant $N_{rom}$, which might be equal to the mathematical $N_{rom}$ for $L^2$ or $H^1$ functional space, %
is likely to be different of the values we find in the following table, %
and we can reasonably thik it will be lesser than its value for the biggest mesh.

\par
For example, $N_{rom}$ for a physical, spherical inclusion will be lesser than $3$, and lesser than $2$ for two spheres per unit cell.

\par
We should consider this issue since $N_{rom}$ may not be too small, if we want ROM to be relevant. %
Indeed, the trivial case when $N_{rom}$ equals $1$ leads us to choose, according to POD's definition, %
the mean value the interpolated $\chi '(,\rho_j)$ for the single POD vector.

\par
Hence resolution of the optimisation problem, directly or with method of snapshots, would be no longer useful.

{\renewcommand{\tabularxcolumn}[1]{%
>{\centering\arraybackslash}m{#1}}

\begin{figure}[H]
%
\begin{center}
%\begin{tabular}{|l||*{5}{c|}}
\begin{tabularx}{0.9\linewidth}%
{|>{\bfseries}c||%
*{3}{c|}%
*{2}{>{\centering \arraybackslash}X|}}
%
\hline
\rowcolor{lightgray} %
Res.%\backslashbox{Res.}{Config.}%
&Single sphere&Single cylinder&Two spheres&%
One sphere, one cylinder, $\rho=$ sphere radius&One sphere, one cylinder, $\rho=$ cylinder radius\\
%
\hline
\hline
10&5&5&4&4&5\\ \hline
20&4&5&3&3&4\\ \hline
50&3&5&2&2&4\\ \hline
\end{tabularx}
\end{center}
%
\caption{Values of $N_{rom}^{99,99\%}$, against the numer of nodes per unit segment}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Résultats et figures de la dimension 3 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{res_disc/res_dim3.tex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Discussion}









